A Fast Unified Model for Parsing and Sentence Understanding

### 2016-06-07 writing/hard_stack_paper/paper.tex
Slight additions to error analysis.

In addition, it seems that tree-structured models, and especially the tree-sequence hybrid models, are more effective than RNNs at extracting informative representations of long sentences. The RNN model falls off in test accuracy more quickly with increasing sentence length than SPINN-PI-NT, which in turn falls of substantially faster than the two hybrid models, repeating a pattern seen more dramatically on artificial data in \citet{bowman2015trees}. For example, all three SPINN models labeled this pair correctly, while the RNN did not:

@@

We suspect that the hybrid nature of the full SPINN model is also responsible for its ability to perform better than an RNN baseline even when its internal parser is relatively ineffective at producing correct full-sentence parses. It may act somewhat like the tree-based CNN, only with access to larger trees: using tree structure to build up local phrase meanings, and then using the tracking LSTM, at least in part, to combine those meanings.

>>>>

In addition, it seems that tree-structured models, and especially the tree-sequence hybrid models, are more effective than RNNs at extracting informative representations of long sentences. The RNN model falls off in test accuracy more quickly with increasing sentence length than SPINN-PI-NT, which in turn falls of substantially faster than the two hybrid models, repeating a pattern seen more dramatically on artificial data in \citet{bowman2015trees}. On pairs with premises of 20 or more words, the RNN's 76.7\% accuracy, while SPINN-PI reaches 80.2\%. All three SPINN models labeled the following example correctly, while the RNN did not:

@@

We suspect that the hybrid nature of the full SPINN model is also responsible for its surprising ability to perform better than an RNN baseline even when its internal parser is relatively ineffective at producing correct full-sentence parses. It may act somewhat like the tree-based CNN, only with access to larger trees: using tree structure to build up local phrase meanings, and then using the tracking LSTM, at least in part, to combine those meanings.
